Alix Thomas, PA & PE lipid interactomics

### 2025-01-09 AT_2025.qmd
Updating site
Minor update to test push

---
title: "Alix Thomas, PA & PE lipid interactomics"
format: html
---

@@

DOI: <https://doi.org/10.1039/D4CC03599B>

## Publication overview

>>>>

---
title: "Alix Thomas, PA & PE lipid interactomics"
format: 
  html:
    embed-resources: true
standalone: true
---

@@

**Authors:**

**Date published:**

**Journal, issue, CRBN:** Chemical Communications

**DOI:** <https://doi.org/10.1039/D4CC03599B>

## Abstract

Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria. Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates. Due to its aromatic caging group, 1 is initial-ly concentrating in perinuclear membranes. After uncaging, rapid translocation to mitochondria was observed. Hence, the tool is useful for tracking PE location and for determining the PE interac-tome. A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.
